---
title: "Current Golf Ratings"
author: "DSMok1"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(magrittr)
summary_table <- read.csv("Recent_Ratings.csv", stringsAsFactors = FALSE) %>%
  select("Rank",
         "Player_Name",
         "Player_Value",
         "Num_Rounds",
         "Num_Rounds_Yr",
         "Country",
         "Tour_Yr"
         )%>%
  mutate_at(vars(Player_Value), funs(round(., 2)))
```

## Summary

This is a super-simple golf rating system.  It's just a straight regression over the past 4 years of golf results, with the most recent results weighted far more heavily.  An exponential weighting system of 0.97 to the "weeks ago" power was used--in other words, results from 1 year ago are weighted at 0.97^52, or 20% as much as this week's results.  The previous years get less and less weight, but are there to provide some stability to the regression for portions of the dataset with more tenuous connections.

The Player Rating is denominated in strokes per round more or less than the average golfer playing on the PGA and European tours.  Players with a minimum of 40 rounds were included and tournament rounds with a minimum of 15 ranked players were included.

## Data

The full output is located at https://github.com/DSMok1/Golf_Ratings_R_V2/blob/master/Output/Recent_Ratings.csv

```{r echo=FALSE, results='asis'}
library(knitr)
kable(summary_table[1:200,], caption="Current Golf Ratings")
```
